---
title: "Finding Out Specific Reasons Behind Missing Bugs During Code Review "
output: html_notebook
---

Author: Arslan Ahmed

Language: R

Tool: RStudio

Date: 01-12-17

Dataset:

We take the following predictive variables into consideration:
1) lines
2) chunks
3) file_count
4) r_queue
5) r_exp
6) r_exp_product
7) s_exp
8) s_exp_product

We predict the following variables:
1) review_time_minutes (how much time does reviewer take to review the code)
2) is_bad (whether his review is good or bad)

We analyze the effect of all the predictor variables on each of the two predicted variables separately.
Purpose is to identify the most important predictor Variables for each of the predicted variables.


```{r}
#read data from CSV file
reviewData <- read.csv("F:/OneDrive - Carleton University/CANADA/Carleton Study/Raman Project/db/newset_6months.csv")
```

```{r}
#remove missing values, if any
reviewData <- na.omit(reviewData)
```

```{r}
#use caret library of R (Classification and Regression Training)
library(caret)
```

```{r}
summary(reviewData)
```

```{r}
set.seed(1)

# Scale predictors.
lines.c = scale(reviewData$lines, center=TRUE, scale=TRUE)
chunks.c = scale(reviewData$chunks, center=TRUE, scale=TRUE)
file_count.c = scale(reviewData$file_count, center=TRUE, scale=TRUE)
r_queue.c = scale(reviewData$r_queue, center=TRUE, scale=TRUE)
r_exp.c = scale(reviewData$r_exp, center=TRUE, scale=TRUE)
r_exp_product.c = scale(reviewData$r_exp_product, center=TRUE, scale=TRUE)
s_exp.c = scale(reviewData$s_exp, center=TRUE, scale=TRUE)
s_exp_product.c = scale(reviewData$s_exp_product, center=TRUE, scale=TRUE)

# bind these new variables into previous data and display a summary.
new.c.vars = cbind(lines.c, chunks.c, file_count.c, r_queue.c, r_exp.c, r_exp_product.c, s_exp.c, s_exp_product.c)
newReviewData = cbind(reviewData, new.c.vars)
names(newReviewData)[11:18] = c("lines.c", "chunks.c", "file_count.c", "r_queue.c", "r_exp.c", "r_exp_product.c", "s_exp.c", "s_exp_product.c")
summary(newReviewData)
```

```{r}
# fit a linear model for is_bad, and run a summary of its results.
modIsBad = lm(is_bad ~ lines.c + chunks.c + file_count.c + r_queue.c + r_exp.c + r_exp_product.c + s_exp.c + s_exp_product.c, data=newReviewData)
summary(modIsBad)
```
Based on the obove outputs, we see that the following are the three most important predictor variables to predict is_bad variable:

1) lines
2) r_exp
3) chunks

```{r}
# fit a linear model for review_time_minutes, and run a summary of its results.
modMinutes = lm(review_time_minutes ~ lines.c + chunks.c + file_count.c + r_queue.c + r_exp.c + r_exp_product.c + s_exp.c + s_exp_product.c, data=newReviewData)
summary(modMinutes)
```

Based on the obove outputs, we see that the following are the three most important predictor variables to predict review_time_minutes variable:

1) s_exp_product
2) r_queue
3) s_exp